Discrete Quantum Theories and Computing

### 2018-02-11 prop_letter_ajhs_referee_response.tex

%\bigskip

\paragraph*{Experimental Data and $\delta$-determinism.} To the best of
our understanding, the argument against $\delta$-determinism by the
referee assumes that the parameter $\delta$ is \emph{exclusively}
related to the density of states defined in a general Hilbert
space. This is indeed Meyer's great insight and the main assumption in
his proof that using the field of rationals nullifies the KS theorem.
In other words, Meyer attributes finite-precision errors to the
description of the states, which is an idea that has been challenged
by several researchers, including Ax and Kochen (as cited by Cabello
2002), who argue that the effect of finite-precision measurements on
the KS theorem requires a different formalization. Our paper, indeed,
makes no particular assumptions about the description of the states,
and attributes finite-precision errors to the measurement process
itself as realized in a laboratory. In our framework, the parameter
$\delta$ reflects insufficient knowledge of the experimenter, which
could be due to a variety of reasons related to imperfections of
devices. A typical question that an experimenter may not be able to
answer accurately would be ``did an electron land in the left half or
the right half of the screen''? There are cases in which the electron
would land too close to the middle of the screen for the experimenter
to be able to determine with certainty that it was left or right of
the center. We simply record this imprecision in the probability we
assign to events, and use the axioms of probability theory
(additivity, convexity, etc) to argue that a sharp transition occurs
when the imprecision reaches a certain value. Our approach is agnostic
about attributing elements of reality to the state function (as
Meyer). We simply attribute lack of certainty to the measured results
through the use of an instrument.

To determine the probability of any event,
we typically repeat an experiment $n$ times and count the number
of times we witness the event. This assumes that for each run of the
experiment we can determine, using our apparatus, whether the event
occurred or not. Assume an event has an ideal mathematical probability
of $0$, and we repeat the experiment $100$ times. In a perfect world
we should be able to refute the event $100$ times and calculate that
the probability is $0$. We might also observe the event $2$ times
and refute it $98$ times and therefore calculate the probability
to be $0.02$. Note that this situation assumes perfect measurement
conditions.
%Let the quantum system be in state~$\ket{\psi}$ and the probability
%of some event  be $0$. Assume we repeat the experiment $100$ times
%and we observe the event $1$ time. The Godsil-Zaks-Meyer approach
%interprets this by assuming that the state was actually $\ket{\psi'}$
%which is infinitesimally close to $\ket{\psi}$ and proceed to reason
%about how coloring the states with rational points relates to the
%coloring of arbitrary states. We make no such assumptions and do not
%impose any constraints on the actual state of the system. In fact
%we do not make any statements about such situations. What we are addressing
%is a situation in which our devices do not allow to make a clear determination
%of whether an event has happened or not. We model this by an uncertainty
%in the probability of the event and then reason using the axioms of
%probability theory to bound this uncertainty. We should add that our
%approach is agnostic about attributing elements of reality to the
%state function (as Meyer). We simply attribute lack of certainty to
%the measured results through the use of an instrument. 
The question we focus on is what happens if we are only able to refute
it $97$ times and are \emph{uncertain} $3$ times? This is quite
common in actual experiments. Mathematically we can model this idea
by stating that the probability of the event is in the range $\left[0,0.03\right]$
which says that the probability of the event could be $0$, $0.01$,
$0.02$, or $0.03$ as each the three missing records could either
be evidence for the event or against it. We just cannot nail it down
given the current experimental results and therefore represent them as a ($\delta=$)$0.03$-deterministic
probability measure. The interesting observation is that the axioms
of probability theory (like additivity and convexity) impose enough
constraints on the structure of probability measures to make them
robust in the face of small $\delta$'s.

To see this in detail, consider a three-dimensional Hilbert space
and an experiment repeated $12$ times. By the KS theorem, it is impossible
to build a probability measure that maps every projection to either
$0=\frac{0}{12}$ or $1=\frac{12}{12}$. Now consider what happens
if $\frac{1}{4}$ of the data for every one-dimensional projector
is missing. A potential account of this degradation is to assign to
each event $P$ the entire range of possibilities $\bar{\mu}_{0}(P)$: 
\begin{center}
\begin{tabular}{cc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{0}\left(P\right)$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$\tabularnewline
\midrule 
\addlinespace
All one-dimensional projectors  & $\left[0,\tfrac{1}{4}\right]$\tabularnewline
\midrule 
\addlinespace
All two-dimensional projectors  & $\left[\tfrac{3}{4},1\right]$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

\noindent This measure is not a valid QIVPM because it does not satisfy
the convexity condition: for any two orthogonal one-dimensional events
$P_{0}$ and $P_{1}$, the convexity condition requires $\bar{\mu}_{0}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}_{0}\left(P_{0}\right)+\bar{\mu}_{0}\left(P_{1}\right)$,
but $\bar{\mu}_{0}\left(P_{0}+P_{1}\right)=\left[\tfrac{3}{4},1\right]$
which is not a subset of $\left[0,\tfrac{1}{2}\right]=\bar{\mu}_{0}\left(P_{0}\right)+\bar{\mu}_{0}\left(P_{1}\right)$.
Interestingly, it is impossible to find any probability measure that
would be consistent with these observations as the interval $\left[\tfrac{3}{4},1\right]$
is completely disjoint from the interval $\left[0,\tfrac{1}{2}\right]$
and no amount of shifting of assumptions regarding the precise outcome
of the missing observations could change that disjointness. However,
a sharp transition occurs when $\delta=\tfrac{1}{3}$ as shown next.

@@

%% Indeed for every one-dimensional projector, the missing
%% data could either refute or support the associated event. 
%% This yields the following probability measure~$\bar{\mu}$
%% as a possible formalization, where the column labeled by $P$ lists
%% projectors, and the column labeled by $\bar{\mu}\left(P\right)$ lists
%% the probability of these projectors.

In case the missing data reaches $\frac{1}{3}$, the probability measure
that assigns to each event the entire range of possibilities is: 
\begin{center}
\begin{tabular}{cc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{1}\left(P\right)$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$\tabularnewline
\midrule 
\addlinespace
All one-dimensional projectors  & $\left[0,\tfrac{1}{3}\right]$\tabularnewline
\midrule 
\addlinespace
All two-dimensional projectors  & $\left[\tfrac{2}{3},1\right]$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

\noindent This is also not a valid probability measure by the same
argument as above. However, in this case $\bar{\mu}_{1}\left(P_{0}+P_{1}\right)=\left[\tfrac{2}{3},1\right]$
and $\left[0,\tfrac{2}{3}\right]=\bar{\mu}_{1}\left(P_{0}\right)+\bar{\mu}_{1}\left(P_{1}\right)$
have a common point. And hence by assuming that the missing data for
one-dimensional projectors always support the associated event, while
those for two-dimensional projectors always refute the event, we can
find the following probability measure which can verified to be a
valid QIVPM and which is consistent with the experimental data: 
\begin{center}
\begin{tabular}{cc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{1}'\left(P\right)$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$\tabularnewline
\midrule 
\addlinespace
All one-dimensional projectors  & $\left[\tfrac{1}{3},\tfrac{1}{3}\right]$\tabularnewline
\midrule 
\addlinespace
All two-dimensional projectors  & $\left[\tfrac{2}{3},\tfrac{2}{3}\right]$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

A similar situation happens when more than $\frac{1}{3}$ of data
is missing. In particular, having half of the data missing, the probability
measure that assigns to each event the entire range of possibilities
is already a QIVPM:
\begin{center}
\begin{tabular}{cc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}_{2}\left(P\right)$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$  & $\imposs$\tabularnewline
\midrule 
\addlinespace
All one-dimensional projectors  & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
\midrule 
\addlinespace
All two-dimensional projectors  & $\left[\tfrac{1}{2},1\right]$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$  & $\necess$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

@@

The above arguments could be summarized and illustrated using the
following figure: 
\begin{center}
\includegraphics[scale=0.5]{prop_letter_ajhs_referee_response_nb} 
\par\end{center}

\noindent The region to the left of the vertical line at $\delta=\frac{1}{3}$
is where we assume small measurement degradation; in that region our
extension of the KS theorem definitely demonstrates contextuality.
In the region to the right, the degradation of the data is large and
our extension of the KS theorem no longer refutes other explanations
for the experimental data.

\bigskip{}

\paragraph*{Mermin-Peres ``Magic Square''.}

We now use this same idea to analyze the Mermin-Peres ``magic square''
argument. We show that when the measurements are infinitely precise,
the Mermin-Peres ``magic square'' argument definitely demonstrates
contextuality. But as we progressively degrade the certainty of the
data, a transition happens in which the Mermin-Peres ``magic square''
argument no longer demonstrates contextuality. Consider the nine observables
$\mathbf{O}_{ij}$ with $i$ and $j$ ranging over $\{0,1,2\}$, corresponding
to the Mermin-Peres ``magic square'' used to illustrate the KS theorem:

{\renewcommand{\arraystretch}{2}% 
\begin{center} 
\begin{tabular}{r|@{\quad}c@{\quad}|@{\quad}c@{\quad}|@{\quad}c@{\quad}|} 
$\mathbf{O}_{ij}$~ & $j=0$ & $j=1$ & $j=2$ \\ 
\hline  
$i=0~$ & $\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline 
\hline  
$i=1~$ & $\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline 
\hline  
$i=2~$ & $\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline 
\hline  
\end{tabular}\,,
\par\end{center} 
}

\noindent The observables are constructed using the Pauli matrices
$\left\{ \mathbb{1},\sigma_{x},\sigma_{y},\sigma_{z}\right\} $ whose
eigenvalues are all either~$1$ or $-1$. They are arranged such
that in each row and column, \emph{except the column $j=2$}, every
observable is the product of the other two, and its expectation value
satisfies 
\begin{eqnarray}
\expval{\mathbf{O}_{i0}}\expval{\mathbf{O}_{i1}} & = & \expval{\mathbf{O}_{i2}}\,,\label{eq:i_expectation_value}\\
\expval{\mathbf{O}_{j2}}\expval{\mathbf{O}_{j2}} & = & \expval{\mathbf{O}_{j2}}\,,\label{eq:j_0_1_expectation_value}
\end{eqnarray}
where $i\in\{0,1,2\}$ and $j\in\{0,1\}$. In the $j=2$ column, we
have instead that $\mathbf{O}_{02}\mathbf{O}_{12}=-\mathbf{O}_{22}$
and 
\begin{equation}
\expval{\mathbf{O}_{02}}\expval{\mathbf{O}_{12}}=-\expval{\mathbf{O}_{22}}\,.\label{eq:j_2_expectation_value}
\end{equation}

Assume we measure each observable twice. By the KS theorem, the following
measurement results are inconsistent with the prediction of quantum
machines because the product of the expectation values in the $j=2$
column violates Eq.~(\ref{eq:j_2_expectation_value}). 
\begin{center}
\begin{tabular}{cccc}
\toprule 
\addlinespace
$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Possible}\\
 & \expval{\mathbf{O}_{ij}}
\end{aligned}
$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $-1$  & $-1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  & $-1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  & $1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$ & $1$  & $1$  & $1$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

Now consider a small potion of experimantal results are missing. For
example, we disgrad the results of $\mathbf{O}_{20}$ , $\mathbf{O}_{22}$
, and $\mathbf{O}_{21}$ in the first trial, and get the following
measurement results:
\begin{center}
\begin{tabular}{ccccc}
\toprule 
\addlinespace
$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
 & \textrm{Might Be}
\end{aligned}
$  & $\begin{aligned} & \textrm{Possible}\\
 & \expval{\mathbf{O}_{ij}}
\end{aligned}
$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbf{O}_{00}$, $\mathbf{O}_{11}$ & $-1$  & $-1$ &  & $-1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  &  & $-1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  &  & $1$\tabularnewline
\midrule 
\addlinespace
\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
\cmidrule{4-5} 
\addlinespace
 &  &  & $-1$ & $0$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

\noindent If all of the missing results are $1$, these experimental
results reduced to the previous case; if any of $\expval{\mathbf{O}_{i2}}$
is $0$, Eq.~(\ref{eq:i_expectation_value}) is violated in the $i$-th
row. Hence, these results are still inconsistent with the prediction
of quantum machines. Similar to the situation that even if $\frac{1}{4}$
of the data is missing, $\bar{\mu}_{0}$cannot be extened to a valid
QIVPM.

Similar situation happens even if we miss a little more data. For
example, the following measurement results is still not consistent
with the prediction of quantum machines.
\begin{center}
\begin{tabular}{ccccc}
\toprule 
\addlinespace
$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
 & \textrm{Might Be}
\end{aligned}
$  & $\begin{aligned} & \textrm{Possible}\\
 & \expval{\mathbf{O}_{ij}}
\end{aligned}
$\tabularnewline
\midrule
\midrule 
\addlinespace
\multirow{2}{*}{$\mathbf{O}_{00}$, $\mathbf{O}_{11}$} & \multirow{2}{*}{$-1$ } & \multirow{2}{*}{$\missing$} & $1$ & $0$\tabularnewline
\cmidrule{4-5} 
\addlinespace
 &  &  & $-1$ & $-1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{01}$, $\mathbf{O}_{10}$ & $-1$  & $-1$  &  & $-1$\tabularnewline
\midrule 
\addlinespace
$\mathbf{O}_{20}$, $\mathbf{O}_{21}$ & $1$  & $1$  &  & $1$\tabularnewline
\midrule 
\addlinespace
\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
\cmidrule{4-5} 
\addlinespace
 &  &  & $-1$ & $0$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

### 2018-02-11 prop_letter_ajhs_referee_response.tex

\noindent However, when we disgrad enough experimental results, the
experimental results would start to be consistent with the prediction
of quantum machines.
\begin{center}
\begin{tabular}{ccccc}
\toprule 
\addlinespace
$\mathbf{O}_{ij}$  & \multicolumn{2}{c}{Results} & $\begin{aligned} & \textrm{Missing}\\
 & \textrm{Might Be}
\end{aligned}
$  & $\begin{aligned} & \textrm{Possible}\\
 & \expval{\mathbf{O}_{ij}}
\end{aligned}
$\tabularnewline
\midrule
\midrule 
\addlinespace
\multirow{2}{*}{$\mathbf{O}_{00}$, $\mathbf{O}_{11}$} & \multirow{2}{*}{$-1$ } & \multirow{2}{*}{$\missing$} & $1$ & $0$\tabularnewline
\cmidrule{4-5} 
\addlinespace
 &  &  & $-1$ & $-1$\tabularnewline
\midrule 
\addlinespace
\multirow{2}{*}{$\mathbf{O}_{01}$, $\mathbf{O}_{10}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$-1$ } & $1$ & $0$\tabularnewline
\cmidrule{4-5} 
\addlinespace
 &  &  & $-1$ & $-1$\tabularnewline
\midrule 
\addlinespace
\multirow{2}{*}{$\mathbf{O}_{20}$, $\mathbf{O}_{21}$} & \multirow{2}{*}{$1$ } & \multirow{2}{*}{$\missing$} & $1$ & $1$\tabularnewline
\cmidrule{4-5} 
\addlinespace
 &  &  & $-1$ & $0$\tabularnewline
\midrule 
\addlinespace
\multirow{2}{*}{$\mathbf{O}_{02}$, $\mathbf{O}_{12}$, $\mathbf{O}_{22}$} & \multirow{2}{*}{$\missing$} & \multirow{2}{*}{$1$} & $1$ & $1$\tabularnewline
\cmidrule{4-5} 
\addlinespace
 &  &  & $-1$ & $0$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

\noindent By suitably assuming the missing data such that the expectation
values of each observables are always $0$, the product relations
among these expectation values is consistent with with the prediction
of quantum machines. This kind of transition from inconsistence to
consistence with the prediction of quantum machines is similar to
the transition from inconsistence to consistence with a QIVPM when
increasing $\delta$ from $<\tfrac{1}{3}$ to $\ge\tfrac{1}{3}$.

### 2018-02-11 prop_letter_ajhs_referee_response.tex

%\bigskip

\paragraph*{Experimental Data and $\delta$-determinism.} To the best of
our understanding, the argument against $\delta$-determinism by the
referee assumes that the parameter $\delta$ is \emph{exclusively}
related to the density of states defined in a general Hilbert
space. This is indeed Meyer's great insight and the main assumption in
his proof that using the field of rationals nullifies the KS theorem.
In other words, Meyer attributes finite-precision errors to the
description of the states, which is an idea that has been challenged
by several researchers, including Ax and Kochen (as cited by Cabello
2002), who argue that the effect of finite-precision measurements on
the KS theorem requires a different formalization. Our paper, indeed,
makes no particular assumptions about the description of the states,
and attributes finite-precision errors to the measurement process
itself as realized in a laboratory. In our framework, the parameter
$\delta$ reflects insufficient knowledge of the experimenter, which
could be due to a variety of reasons related to imperfections of
devices. A typical question that an experimenter may not be able to
answer accurately would be ``did an electron land in the left half or
the right half of the screen''? There are cases in which the electron
would land too close to the middle of the screen for the experimenter
to be able to determine with certainty that it was left or right of
the center. We simply record this imprecision in the probability we
assign to events, and use the axioms of probability theory
(additivity, convexity, etc) to argue that a sharp transition occurs
when the imprecision reaches a certain value. Our approach is agnostic
about attributing elements of reality to the state function (as
Meyer). We simply attribute lack of certainty to the measured results
through the use of an instrument.

To determine the probability of any event,
we typically repeat an experiment $n$ times and count the number
of times we witness the event. This assumes that for each run of the
experiment we can determine, using our apparatus, whether the event
occurred or not. Assume an event has an ideal mathematical probability
of $0$, and we repeat the experiment $100$ times. In a perfect world
we should be able to refute the event $100$ times and calculate that
the probability is $0$. We might also observe the event $2$ times
and refute it $98$ times and therefore calculate the probability
to be $0.02$. Note that this situation assumes perfect measurement
conditions.
%Let the quantum system be in state~$\ket{\psi}$ and the probability
%of some event  be $0$. Assume we repeat the experiment $100$ times
%and we observe the event $1$ time. The Godsil-Zaks-Meyer approach
%interprets this by assuming that the state was actually $\ket{\psi'}$
%which is infinitesimally close to $\ket{\psi}$ and proceed to reason
%about how coloring the states with rational points relates to the
%coloring of arbitrary states. We make no such assumptions and do not
%impose any constraints on the actual state of the system. In fact
%we do not make any statements about such situations. What we are addressing
%is a situation in which our devices do not allow to make a clear determination
%of whether an event has happened or not. We model this by an uncertainty
%in the probability of the event and then reason using the axioms of
%probability theory to bound this uncertainty. We should add that our
%approach is agnostic about attributing elements of reality to the
%state function (as Meyer). We simply attribute lack of certainty to
%the measured results through the use of an instrument. 
The question we focus on is what happens if we are only able to refute
it $97$ times and are \emph{uncertain} $3$ times? This is quite
common in actual experiments. Mathematically we can model this idea
by stating that the probability of the event is in the range $\left[0,0.03\right]$
which says that the probability of the event could be $0$, $0.01$,
$0.02$, or $0.03$ as each the three missing records could either
be evidence for the event or against it. We just cannot nail it down
given the current experimental results and therefore represent them as a ($\delta=$)$0.03$-deterministic
probability measure. The interesting observation is that the axioms
of probability theory (like additivity and convexity) impose enough
constraints on the structure of probability measures to make them
robust in the face of small $\delta$'s.

@@

A similar situation happens when more than $\frac{1}{3}$ of data is
missing. In particular, having half of the data missing, the
probability measure that assigns to each event the entire range of
possibilities is already a QIVPM:

\begin{center}
\begin{tabular}{cc}
\toprule 
\addlinespace
$P$  & $\bar{\mu}\left(P\right)$\tabularnewline
\midrule
\midrule 
\addlinespace
$\mathbb{0}$ & $\imposs$\tabularnewline
\midrule 
\addlinespace
All one-dimensional projectors & $\left[0,\tfrac{1}{2}\right]$\tabularnewline
\midrule 
\addlinespace
All two-dimensional projectors & $\left[\tfrac{1}{2},1\right]$\tabularnewline
\midrule 
\addlinespace
$\mathbb{1}$ & $\necess$\tabularnewline
\bottomrule
\end{tabular}
\par\end{center}

The above arguments could be summarized and illustrated using the following figure: 
\begin{center}
\includegraphics[scale=0.5]{prop_letter_ajhs_referee_response_nb}
\par\end{center}

\noindent The region to the left of the vertical line at
$\delta=\frac{1}{3}$ is where we assume small measurement degradation;
in that region our extension of the KS theorem definitely demonstrates
contextuality ({\bf{\sf C}}). In the region to the right, the degradation of the data
is large and our extension of the KS theorem no longer refutes other
explanations for the experimental data.
